---
title: "Plasmid OE with STING Inhibition"
subtitle: "Figure 1: Dose-dependent effects of STING pathway inhibitors on plasmid over-expression in HAECs."
author: "Shuai Yuan"
date: '`r format(Sys.Date(), "%Y-%m-%d")`'
output: 
  html_document:
    toc: true
    toc_float: true
    toc_depth: 5
    number_sections: true
---

```{r setup, echo = FALSE}
options(
  htmltools.dir.version = FALSE, 
  knitr.duplicate.label = "allow", 
  ggpattern_res = 1200
  )
knitr::opts_chunk$set(
  dpi = 300, 
  out.width = "100%",
  cache = FALSE,
  echo = FALSE,
  message = FALSE, 
  warning = FALSE,
  hiline = TRUE
  )

root_dir <- "../Data/WB"
```

```{r pkgs}
library(lmerTest)
library(emmeans)

library(openxlsx)
library(tidyverse)
library(magrittr)
library(extrafont)
library(glue)
library(ggpattern)
library(ggupset)
library(patchwork)
# library(ggtext)

# Define ggplot theme

fontSize <- 10
lineWidth <- 0.4 # also used in setting geom with linewidth. 

theme_yuan_wb <- function(baseFontSize = fontSize, baseLineWidth = lineWidth) {
  font <- "serif"
  
  theme_classic() %+replace%
    
    theme(
      panel.grid = element_blank(),
      panel.border = element_blank(),
      plot.background = element_blank(), 
      plot.margin = margin(0, 0, 0, 0), 
      
      axis.line = element_blank(),
      axis.ticks = element_blank(),

      text = element_text(size = baseFontSize), 
      line = element_line(linewidth = baseLineWidth), 
      
      axis.text.x = element_text(angle = 45, hjust = 0),
      legend.position = 'none',
      # aspect.ratio = 0.25,
      
      title = element_text(
        family = font,
        face = "bold",
        size = baseFontSize
      ),
      
      axis.title = element_text(
        family = font,
        face = "bold",
        size = baseFontSize
      ),
      
      axis.text = element_text(
        family = font,
        face = "bold",
        size = baseFontSize * 0.8
      ),
      
      legend.title = element_text(
        family = font,
        face = "bold",
        size = baseFontSize
      ),
      
      legend.text = element_text(
        family = font,
        face = "bold",
        size = baseFontSize * 0.8
      ),
      
      strip.background = element_blank(),
      strip.placement = "outside", 
      strip.text = element_text(
        family = font,
        face = "bold",
        size = baseFontSize
      )
    )
}

theme_yuan <- function(baseFontSize = fontSize, baseLineWidth = lineWidth) {
  font <- "sans"
  
  theme_classic() %+replace%
    
    theme(
      panel.grid.major = element_blank(),
      panel.grid.minor = element_blank(),
      plot.margin = margin(2, 0, 2, 0), 
      
      text = element_text(size = baseFontSize), 
      line = element_line(linewidth = baseLineWidth), 

      # axis.line = element_line(color = "black", linewidth = baseLineWidth),
      # axis.ticks = element_line(color = "black", linewidth = baseLineWidth),
      axis.ticks.length = unit(baseLineWidth * 2, "mm"),
      
      
      axis.title = element_text(
        family = font,
        face = "bold",
        size = baseFontSize
      ),
      
      axis.text = element_text(
        family = font,
        face = "bold",
        size = baseFontSize * 0.8
      ),
      
      legend.title = element_text(
        family = font,
        face = "bold",
        size = baseFontSize
      ),
      
      legend.text = element_text(
        family = font,
        face = "bold",
        size = baseFontSize * 0.8
      ),
      
      strip.placement = "outside", 
      strip.background = element_blank(),
      strip.text = element_text(
        family = font,
        face = "bold",
        size = baseFontSize
      )
    )
}

cropBlot <- function(target, imgPath, x, y, width, height, ...) {
  library(magick)
  
  format <- "tif"
  
  img <- image_read(imgPath)
  imgInfo <- image_info(img)
  imgWidth <- imgInfo$width
  imgHeight <- imgInfo$height
  
  cropWidth <- imgWidth * width
  cropHeight <- imgHeight * height
  
  xOff <- x * imgWidth
  yOff <- y * imgHeight
  
  imgCropped <-
    image_crop(img, glue("{cropWidth}x{cropHeight}+{xOff}+{yOff}>"))
  
  # ggpattern calls gridpattern:::img_read. The function requires image to have 4 channels. 
  # When magick::image::write is called to write PNG, optimization collapses RGB to grayscale as the blot has only grayscale information. 
  # This behavior doesn't seem to be overridden in R. 
  
  imgCropped <- image_convert(imgCropped, format = format, type = "truecolor", colorspace = "sRGB")
  
  imgSavePath <-
    gsub(paste0(".", tools::file_ext(imgPath)), paste0("_", target), imgPath)
  
  image_write(imgCropped, paste0(imgSavePath, ".", format), format = format)
  return(paste0(imgSavePath, ".", format))
}

pltSpacer <- plot_spacer() + theme(plot.margin = margin(0, 0, 0, 0))

# stdError <- function(x) sd(x)/sqrt(length(x))

getStatAnnotTbl <- function(dfData, dfStat){
  Ypad <-  (fontSize/ggplot2::.pt+2) * max(dfData$Value) * 0.025

  dfStat <- dfStat %>%
    arrange(Group1, Group2) %>%
    mutate(
      Ypad = Ypad, 
      Ymin1 = map_dbl(Group1, function(x) {
        dfData %>% filter(Group == x) %>% pull(Value) %>% max()
        }), 
      Ymin2 = map_dbl(Group2, function(x) {
        dfData %>% filter(Group == x) %>% pull(Value) %>% max()
        }),
      Ymax = map2_dbl(Group1, Group2, function(x, y){
        dfData %>% filter(Group >= x & Group <= y) %>% pull(Value) %>% max()
        })
      ) %>%
    rowwise() %>%
    mutate(
      Ymin1 = Ymin1 + Ypad / 2, 
      Ymin2 = Ymin2 + Ypad / 2, 
      X = sum(which(levels(dfData$Group) %in% c(Group1, Group2)))/2
    )

  if (nrow(dfStat) > 1) {
    for (i in 2:nrow(dfStat)){
      for (j in 1:(i-1)){
        if (dfStat$Ymax[i] <= dfStat$Ymax[j] + Ypad){
          if ((dfStat$Group2[j] > dfStat$Group1[i] | dfStat$Group2[j] > dfStat$Group1[i])) {
            dfStat[i, "Ymax"] <- dfStat$Ymax[i-1] + Ypad
          }
        }
      }
    }    
  }
  
  dfStat <- dfStat %>%
    mutate(
      YmaxAdj = Ymax + Ypad,
      XAdj = X
    )
  
  for (i in 1:nrow(dfStat)){
      dfStat[i, "XAdj"] <- dfStat$XAdj[i]
    if (floor(dfStat$XAdj[i]) == dfStat$XAdj[i]) {
      if (levels(dfData$Group)[as.integer(dfStat$XAdj[i])] %in% c(dfStat$Group1, dfStat$Group2)){
        dfStat[i, "XAdj"] <-  dfStat$XAdj[i]-1/length(levels(dfData$Group))
      }
    }
  }
  
  return(dfStat)
}
```

# **Panel A: MRT67307 dose-response**

Letter paper size: 8.5 in * 11 in
Plos One figure size: width 2.63 in - 7.5 in; single column figure width <= 5.2 in; height <= 8.75
Text within figures: 8-12 pt. 

## Representative blot

```{r fig.height=1, fig.width=3.75}
blnForget <- memoise::forget(gridpattern:::img_read_memoised)
dfBlot <- data.frame(
  target = c("CYB5R4", "GFP", "aTubulin")
) %>%
  mutate(
    target = factor(target, levels = target), 
    imgPath = c(
      glue("{root_dir}/20230215_HAEC_pCIGX-R4_OE0.4ug_12well_MRT67307_BX795_20uM_0.5dilutions/20230215_MRT67307_CYB5R4.tif"),
      glue("{root_dir}/20230215_HAEC_pCIGX-R4_OE0.4ug_12well_MRT67307_BX795_20uM_0.5dilutions/20230215_MRT67307_GFP.tif"),
      glue("{root_dir}/20230215_HAEC_pCIGX-R4_OE0.4ug_12well_MRT67307_BX795_20uM_0.5dilutions/20230215_MRT67307_aTub.tif")),
    x = c(0.07, 0.065, 0.08), 
    y = c(0.38, 0.7, 0.38), 
    width = c(0.87, 0.86, 0.85), 
    height = c(0.15, 0.1, 0.15), 
    lane = 12
  )

vtSample <- c(0, 0, 20*0.5^c(9:0)) %>%
  formatC(digits = 2, format = "fg", flag = "#") %>%
  str_replace("\\.$", "")
vtSample <- paste("MRT67307", vtSample, "uM")
vtSample <- paste(vtSample, "+", c("Vehicle", rep("pCIGX-CYB5R4", times = 11)))

imgCropped <- pmap_chr(dfBlot, cropBlot)
dfBlot$cropped <- imgCropped
names(imgCropped) <- dfBlot$target

pltBlot <- dfBlot %>%
  ggplot(aes(x = lane, y = target)) + 
  geom_col_pattern(
    aes(pattern_filename = target), 
    pattern = "image",
    pattern_type = "squish",
    color = "black",
    linewidth = lineWidth,
    pattern_scale = 1
  ) +
  scale_pattern_filename_manual(values = imgCropped) +
  labs(x = NULL, y = NULL) +
  scale_x_continuous(position = "top", limits = c(0, length(vtSample)), breaks = c(1:length(vtSample) - 0.5), labels = vtSample, expand = c(0, 0)) +
  scale_y_discrete(limits=rev) +
  coord_cartesian(clip = "off") +
  theme_yuan_wb(baseFontSize = 10) +
  theme(
    axis.text.x = element_blank()
  )

pltMw <- data.frame(
  target = factor(dfBlot$target, levels = dfBlot$target), 
  kDa = c(55, 27, 51)
) %>%
  ggplot(aes(x = 0, y = target, label = kDa)) +
  geom_text(size = 8/ggplot2::.pt) +
  theme_yuan_wb(baseFontSize = 10) +
  labs(x = "kDa", y = NULL) +
  scale_x_discrete(position = "top") +
  coord_cartesian(clip = "off") +
  theme(
    axis.text.x = element_blank(), 
    axis.text.y = element_blank()
  )

pltBlotMRT <- pltBlot + pltMw + plot_layout(widths = c(9, 0.5))

show(pltBlotMRT)
```

## Quantification

```{r, fig.height=2.5, fig.width=3.75}
file.list <- list.files(glue("{root_dir}"), pattern = "\\.xlsx$", full.names = TRUE, recursive = TRUE)
file.list <- file.list[grepl("0-20uM|dilution", file.list)]
file.list <- file.list[grepl("HAEC", file.list)]

dfData <- map_dfr(file.list, read.xlsx) %>%
  filter(Inhibitor.Name == "MRT67307") %>%
  arrange(Date) %>%
  mutate(
    Target = fct_inorder(Target), 
    Inhibitor.uM = formatC(Inhibitor.uM, digits = 1, format = "fg", flag = "#") %>%
  str_replace("\\.$", "") %>% as.character(Inhibitor.uM), 
    Inhibitor.uM = fct_inorder(Inhibitor.uM), 
    Group = paste(Inhibitor.uM, Plasmid), 
    Group = fct_inorder(Group) %>% ordered()
    ) %>%
  arrange(Date, Target, Lane) %>%
  group_by(Date) %>%
  mutate(
    Signal.Norm = Signal / Signal[Target == "a-Tubulin"]
  ) %>%
  group_by(Date, Target) %>%
  mutate(
    Value = Signal.Norm / Signal.Norm[Lane == 1]
  ) %>%
  ungroup()

dfStat <- dfData %>%
  filter(Target != "a-Tubulin") %>%
  group_by(Target) %>%
  nest() %>%
  mutate(
    model = map(data, function(x) aov(Value ~ Group, data = x)),
    Anova.pvalue = map_dbl(model, function(x) summary(x)[[1]]$`Pr(>F)`[1])
    # model = map(data, function(x) lmer(Value ~ Group + (1|Date), data = x)), 
    # Anova.pvalue = map_dbl(model, function(x) anova(x)$`Pr(>F)`[1])
  ) %>%
  filter(Anova.pvalue < 0.05) %>%
  mutate(
    post.hoc = map2(data, model, function(x, y){
      emm <- emmeans(y, ~ Group)
      dfPostHoc <- contrast(emm, "pairwise", adjust = "tukey") %>%
        as.data.frame() %>%
        rename(c("Contrast" = "contrast")) %>%
        # The groups need to be in the levels of dfData$Group.
        # Group1 and Group2 are two factors sharing the same order as dfData$Group. 
        mutate(
          Contrast = as.character(Contrast) %>%
            str_replace_all(c("^\\(" = "", "\\)$" = "", "\\) - \\(" = "SPLIT", " - \\(" = "SPLIT", "\\) - " = "SPLIT")), 
          Group1 = map_vec(Contrast, function(x) {
            str_split_1(x, "SPLIT") %>% 
              ordered(levels = levels(dfData$Group)) %>%
              min()
            }),
          Group2 = map_vec(Contrast, function(x) {
            vt <- str_split_1(x, "SPLIT") %>% 
              ordered(levels = levels(dfData$Group)) %>%
              max()
            }),
          Contrast = str_replace_all(Contrast, c("SPLIT" = " vs "))
          ) %>% 
        # Post-hoc table should be cleaned up before coordinates are calculated. 
        filter(p.value < 0.05 & ("0 pCIGX-hCYB5R4" == Group1 | "0 pCIGX-hCYB5R4" == Group2))

      if (nrow(dfPostHoc) == 0) return()

      getStatAnnotTbl(x, dfPostHoc)
    })
  ) %>%
  unnest(cols = c("post.hoc")) %>%
  ungroup()

lstPltBar <- dfData %>%
  filter(Target != "a-Tubulin") %>%
  group_by(Target) %>%
  nest() %>%
  mutate(
    plt = map(data, function(x){
      p <- ggplot(x, aes(x = Group, y = Value)) +
        stat_summary(geom = "col", fun.data = "mean_se", aes(fill = Group), color = "black", linewidth = lineWidth) +
        stat_summary(geom = "errorbar", fun.data = "mean_se", width = 0.5, linewidth = lineWidth) +
        scale_fill_brewer(palette = "Set3") +
        annotation_custom(grob = grid::textGrob(label = glue("{unique(Target)}\n(Fold Change)"), rot = 90,  gp = grid::gpar(fontsize = 8, fontface = "bold"), x = -30, default.units = "pt")) + 
        geom_point(size = 1) +
        guides(fill = FALSE) +
        coord_cartesian(clip = "off") +
        scale_y_continuous(expand = expansion(mult = c(0, 0.1))) +
        theme_yuan(baseFontSize = 10) +
        theme(
          axis.text.x = element_blank(),
          axis.ticks.x = element_blank(),
          axis.title = element_blank(), 
          plot.background = element_blank()
        )
      
      if (nrow(dfStat) > 0) {
        p <- p  +
          geom_segment(data = dfStat[dfStat$Target == unique(Target), ], aes(x = Group1, y = YmaxAdj, xend = Group2, yend = YmaxAdj), linewidth = lineWidth) +
          geom_segment(data = dfStat[dfStat$Target == unique(Target), ], aes(x = Group1, y = Ymin1, xend = Group1, yend = YmaxAdj), linewidth = lineWidth) +
          geom_segment(data = dfStat[dfStat$Target == unique(Target), ], aes(x = Group2, y = Ymin2, xend = Group2, yend = YmaxAdj), linewidth = lineWidth) +
          geom_text(data = dfStat[dfStat$Target == unique(Target), ], aes(x = XAdj, y = YmaxAdj + Ypad * 0.1, label = ifelse(p.value < 0.05, "*", "")), size = fontSize/ggplot2::.pt+2)
      }
        p <- p + pltSpacer + plot_layout(widths = c(9, 0.5))
    })
  ) %>%
  ungroup %>%
  select(plt) %>%
  unlist(recursive = FALSE, use.names = TRUE)

pltBarMRT <- wrap_plots(lstPltBar, nrow = 2)

pltBarMRT
```

## Legend

```{r fig.height=0.8, fig.width=3.75}
pltTbl <- data.frame(
  sample = vtSample, 
  "pCIGX-CYB5R4 (ug)" = c("0", rep("0.2", times = 11)), 
  "MRT67307 (uM)" = c(0, 0, 20*0.5^c(9:0)) %>%
  formatC(digits = 1, format = "fg", flag = "#") %>%
  str_replace("\\.$", ""), 
  check.names = FALSE
) %>%
  mutate(sample = factor(vtSample, levels = vtSample)) %>%
  pivot_longer(cols = names(.)[2:3], names_to = "treatment") %>%
  ggplot(aes(x = sample, y = treatment, label = value)) +
  geom_text(size = 8/ggplot2::.pt, angle = 45, hjust = 1) +
  # geom_hline(yintercept = 1.5, linewidth = 0.2, color = "gray") +
  # geom_vline(xintercept = c(1:11) + 0.5, linewidth = 0.2, color = "gray") +
  labs(y = NULL, x = NULL) +
  coord_cartesian(clip = "off") +
  theme_yuan_wb(baseFontSize = 10) +
  theme(
    axis.text.x = element_blank()
    # panel.border = element_rect(fill = NA, color = "gray")
  )

pltTblMRT <- (pltTbl + pltSpacer) + plot_layout(widths = c(9, 0.5))

show(pltTblMRT)
```

```{r fig.height=3.3, fig.width=3.75}
pltA <- (pltBlotMRT / pltBarMRT / pltTblMRT) + plot_layout(height = c(1, 2.5, 0.8), ncol = 1)

show(pltA)

# ggsave("Figure_1A.pdf", pltA, height = 3.3, width = 3.75)
```

# **Panel B: BX795 dose-response**

Letter paper size: 8.5 in * 11 in
Plos One figure size: width 2.63 in - 7.5 in; single column figure width <= 5.2 in; height <= 8.75
Text within figures: 8-12 pt. 

## Representative blot

```{r fig.height=1, fig.width=3.75}
blnForget <- memoise::forget(gridpattern:::img_read_memoised)
dfBlot <- data.frame(
  target = c("CYB5R4", "GFP", "aTubulin")
) %>%
  mutate(
    target = factor(target, levels = target), 
    imgPath = c(
      glue("{root_dir}/20230215_HAEC_pCIGX-R4_OE0.4ug_12well_MRT67307_BX795_20uM_0.5dilutions/20230215_BX795_CYB5R4.tif"), 
      glue("{root_dir}/20230215_HAEC_pCIGX-R4_OE0.4ug_12well_MRT67307_BX795_20uM_0.5dilutions/20230215_BX795_GFP.tif"),
      glue("{root_dir}/20230215_HAEC_pCIGX-R4_OE0.4ug_12well_MRT67307_BX795_20uM_0.5dilutions/20230215_BX795_aTub.tif")),
    x = c(0.065, 0.065, 0.065), 
    y = c(0.38, 0.67, 0.38), 
    width = c(0.86, 0.85, 0.85), 
    height = c(0.15, 0.1, 0.15), 
    lane = 12
  )

vtSample <- c(0, 0, 20*0.5^c(9:0)) %>%
  formatC(digits = 2, format = "fg", flag = "#") %>%
  str_replace("\\.$", "")
vtSample <- paste("MRT67307", vtSample, "uM")
vtSample <- paste(vtSample, "+", c("Vehicle", rep("pCIGX-CYB5R4", times = 11)))

imgCropped <- pmap_chr(dfBlot, cropBlot)
dfBlot$cropped <- imgCropped
names(imgCropped) <- dfBlot$target


pltBlot <- dfBlot %>%
  ggplot(aes(x = lane, y = target)) + 
  geom_col_pattern(
    aes(pattern_filename = target), 
    pattern = "image",
    pattern_type = "squish",
    color = "black",
    linewidth = lineWidth, 
    pattern_scale = 1
  ) +
  scale_pattern_filename_manual(values = imgCropped) +
  labs(x = NULL, y = NULL) +
  scale_x_continuous(position = "top", limits = c(0, length(vtSample)), breaks = c(1:length(vtSample) - 0.5), labels = vtSample, expand = c(0, 0)) +
  scale_y_discrete(limits=rev) +
  coord_cartesian(clip = "off") +
  theme_yuan_wb(baseFontSize = 10) +
  theme(
    axis.text.x = element_blank()
  )

pltMw <- data.frame(
  target = factor(dfBlot$target, levels = dfBlot$target), 
  kDa = c(55, 27, 51)
) %>%
  ggplot(aes(x = 0, y = target, label = kDa)) +
  geom_text(size = 8/ggplot2::.pt) +
  theme_yuan_wb(baseFontSize = 10) +
  labs(x = "kDa", y = NULL) +
  scale_x_discrete(position = "top") +
  coord_cartesian(clip = "off") +
  theme(
    axis.text.x = element_blank(), 
    axis.text.y = element_blank()
  )

pltBlotBX <- pltBlot + pltMw + plot_layout(widths = c(9, 0.5))

show(pltBlotBX)
```

## Quantification

```{r, fig.height=2.5, fig.width=3.75}
file.list <- list.files(glue("{root_dir}"), pattern = "\\.xlsx$", full.names = TRUE, recursive = TRUE)
file.list <- file.list[grepl("0-20uM|dilution", file.list)]
file.list <- file.list[grepl("HAEC", file.list)]

dfData <- map_dfr(file.list, read.xlsx) %>%
  filter(Inhibitor.Name == "BX795") %>%
  arrange(Date) %>%
  mutate(
    Target = fct_inorder(Target), 
    Inhibitor.uM = formatC(Inhibitor.uM, digits = 1, format = "fg", flag = "#") %>%
  str_replace("\\.$", "") %>% as.character(Inhibitor.uM), 
    Inhibitor.uM = fct_inorder(Inhibitor.uM), 
    Group = paste(Inhibitor.uM, Plasmid), 
    Group = fct_inorder(Group) %>% ordered()
    ) %>%
  arrange(Date, Target, Lane) %>%
  group_by(Date) %>%
  mutate(
    Signal.Norm = Signal / Signal[Target == "a-Tubulin"]
  ) %>%
  group_by(Date, Target) %>%
  mutate(
    Value = Signal.Norm / Signal.Norm[Lane == 1]
  )

dfStat <- dfData %>%
  filter(Target != "a-Tubulin") %>%
  group_by(Target) %>%
  nest() %>%
  mutate(
    model = map(data, function(x) aov(Value ~ Group, data = x)),
    Anova.pvalue = map_dbl(model, function(x) summary(x)[[1]]$`Pr(>F)`[1])
    # model = map(data, function(x) lmer(Value ~ Group + (1|Date), data = x)),
    # Anova.pvalue = map_dbl(model, function(x) anova(x)$`Pr(>F)`[1])
  ) %>%
  filter(Anova.pvalue < 0.05) %>%
  mutate(
    post.hoc = map2(data, model, function(x, y){
      emm <- emmeans(y, ~ Group)
      dfPostHoc <- contrast(emm, "pairwise", adjust = "tukey") %>%
        as.data.frame() %>%
        rename(c("Contrast" = "contrast")) %>%
        # The groups need to be in the levels of dfData$Group.
        # Group1 and Group2 are two factors sharing the same order as dfData$Group. 
        mutate(
          Contrast = as.character(Contrast) %>%
            str_replace_all(c("^\\(" = "", "\\)$" = "", "\\) - \\(" = "SPLIT", " - \\(" = "SPLIT", "\\) - " = "SPLIT")), 
          Group1 = map_vec(Contrast, function(x) {
            str_split_1(x, "SPLIT") %>% 
              ordered(levels = levels(dfData$Group)) %>%
              min()
            }),
          Group2 = map_vec(Contrast, function(x) {
            vt <- str_split_1(x, "SPLIT") %>% 
              ordered(levels = levels(dfData$Group)) %>%
              max()
            }),
          Contrast = str_replace_all(Contrast, c("SPLIT" = " vs "))
          ) %>% 
        # Post-hoc table should be cleaned up before coordinates are calculated. 
        filter(p.value < 0.05 & ("0 pCIGX-hCYB5R4" == Group1 | "0 pCIGX-hCYB5R4" == Group2))

      if (nrow(dfPostHoc) == 0) return()

      getStatAnnotTbl(x, dfPostHoc)
    })
  ) %>%
  unnest(cols = c("post.hoc")) %>%
  ungroup()

lstPltBar <- dfData %>%
  filter(Target != "a-Tubulin") %>%
  group_by(Target) %>%
  nest() %>%
  mutate(
    plt = map(data, function(x){
      p <- ggplot(x, aes(x = Group, y = Value)) +
        stat_summary(geom = "col", fun.data = "mean_se", aes(fill = Group), color = "black", linewidth = lineWidth) +
        stat_summary(geom = "errorbar", fun.data = "mean_se", width = 0.5, linewidth = lineWidth) +
        scale_fill_brewer(palette = "Set3") +
        annotation_custom(grob = grid::textGrob(label = glue("{unique(Target)}\n(Fold Change)"), rot = 90,  gp = grid::gpar(fontsize = 8, fontface = "bold"), x = -30, default.units = "pt")) + 
        geom_point(size = 1) +
        guides(fill = FALSE) +
        coord_cartesian(clip = "off") +
        scale_y_continuous(expand = expansion(mult = c(0, 0.1))) +
        theme_yuan(baseFontSize = 10) +
        theme(
          axis.text.x = element_blank(),
          axis.ticks.x = element_blank(), 
          axis.title = element_blank(), 
          plot.background = element_blank()
        )
      
      if (nrow(dfStat) > 0) {
        p <- p  +
          geom_segment(data = dfStat[dfStat$Target == unique(Target), ], aes(x = Group1, y = YmaxAdj, xend = Group2, yend = YmaxAdj), linewidth = lineWidth) +
          geom_segment(data = dfStat[dfStat$Target == unique(Target), ], aes(x = Group1, y = Ymin1, xend = Group1, yend = YmaxAdj), linewidth = lineWidth) +
          geom_segment(data = dfStat[dfStat$Target == unique(Target), ], aes(x = Group2, y = Ymin2, xend = Group2, yend = YmaxAdj), linewidth = lineWidth) +
          geom_text(data = dfStat[dfStat$Target == unique(Target), ], aes(x = XAdj, y = YmaxAdj + Ypad * 0.1, label = ifelse(p.value < 0.05, "*", "")), size = fontSize/ggplot2::.pt+2)
      }
      
      p <- p + pltSpacer + plot_layout(widths = c(9, 0.5))
    })
  ) %>%
  ungroup %>%
  select(plt) %>%
  unlist(recursive = FALSE, use.names = TRUE)

pltBarBX <- wrap_plots(lstPltBar, nrow = 2)

pltBarBX
```

## Legend

```{r fig.height=0.8, fig.width=3.75}
pltTbl <- data.frame(
  sample = vtSample, 
  "pCIGX-CYB5R4 (ug)" = c("0", rep("0.2", times = 11)), 
  "BX795 (uM)" = c(0, 0, 20*0.5^c(9:0)) %>%
  formatC(digits = 1, format = "fg", flag = "#") %>%
  str_replace("\\.$", ""), 
  check.names = FALSE
) %>%
  mutate(sample = factor(vtSample, levels = vtSample)) %>%
  pivot_longer(cols = names(.)[2:3], names_to = "treatment") %>%
  ggplot(aes(x = sample, y = treatment, label = value)) +
  geom_text(size = 8/ggplot2::.pt, angle = 45, hjust = 1) +
  # geom_hline(yintercept = 1.5, linewidth = 0.2, color = "gray") +
  # geom_vline(xintercept = c(1:11) + 0.5, linewidth = 0.2, color = "gray") +
  labs(y = NULL, x = NULL) +
  coord_cartesian(clip = "off") +
  theme_yuan_wb(baseFontSize = 10) +
  theme(
    axis.text.x = element_blank()
    # panel.border = element_rect(fill = NA, color = "gray")
  )

pltTblBX <- (pltTbl + pltSpacer) + plot_layout(widths = c(9, 0.5))

show(pltTblBX)
```

```{r fig.height=3.3, fig.width=3.75}
pltB <- (pltBlotBX / pltBarBX / pltTblBX) + plot_layout(height = c(1, 2.5, 0.8), ncol = 1)

show(pltB)

# ggsave("Figure_1B", pltB, height = 3.3, width = 3.75)
```

# Figure 1 Assembly

```{r fig.height=3.3, fig.width=7.5}
(pltA | pltB) +
  plot_annotation(tag_levels = list(c("A", "", "", "", "", 
                                 "B", "", "", "", ""))) &
  theme(
    plot.tag.position = c(0.1, 0.9), 
    plot.background = element_blank()
    )

ggsave("Figure_1_v1.1.pdf", width = 7.5, height = 3.3, dpi = 600)
```


