---
title: "Plasmid OE with STING Inhibition"
subtitle: "Figure 2: Plasmid gene expression after MRT67307 withdrawal"
author: "Shuai Yuan"
date: '`r format(Sys.Date(), "%Y-%m-%d")`'
output: 
  html_document:
    toc: true
    toc_float: true
    toc_depth: 5
    number_sections: true
---

```{r setup, echo = FALSE}
options(
  htmltools.dir.version = FALSE, 
  knitr.duplicate.label = "allow", 
  ggpattern_res = 1200
  )
knitr::opts_chunk$set(
  dpi = 300, 
  out.width = "100%",
  cache = FALSE,
  echo = FALSE,
  message = FALSE, 
  warning = FALSE,
  hiline = TRUE
  )

root_dir <- "../Data/WB"
```

```{r pkgs}
library(lmerTest)
library(emmeans)

library(openxlsx)
library(tidyverse)
library(magrittr)
library(extrafont)
library(glue)
library(ggpattern)
library(ggupset)
library(patchwork)
# library(ggtext)

# Define ggplot theme

fontSize <- 10
lineWidth <- 0.4 # also used in setting geom with linewidth. 

theme_yuan_wb <- function(baseFontSize = fontSize, baseLineWidth = lineWidth) {
  font <- "serif"
  
  theme_classic() %+replace%
    
    theme(
      panel.grid = element_blank(),
      panel.border = element_blank(),
      plot.background = element_blank(), 
      plot.margin = margin(0, 0, 0, 0), 
      
      axis.line = element_blank(),
      axis.ticks = element_blank(),

      text = element_text(size = baseFontSize), 
      line = element_line(linewidth = baseLineWidth), 
      
      axis.text.x = element_text(angle = 45, hjust = 0),
      legend.position = 'none',
      # aspect.ratio = 0.25,
      
      title = element_text(
        family = font,
        face = "bold",
        size = baseFontSize
      ),
      
      axis.title = element_text(
        family = font,
        face = "bold",
        size = baseFontSize
      ),
      
      axis.text = element_text(
        family = font,
        face = "bold",
        size = baseFontSize * 0.8
      ),
      
      legend.title = element_text(
        family = font,
        face = "bold",
        size = baseFontSize
      ),
      
      legend.text = element_text(
        family = font,
        face = "bold",
        size = baseFontSize * 0.8
      ),
      
      strip.background = element_blank(),
      strip.placement = "outside", 
      strip.text = element_text(
        family = font,
        face = "bold",
        size = baseFontSize
      )
    )
}

theme_yuan <- function(baseFontSize = fontSize, baseLineWidth = lineWidth) {
  font <- "sans"
  
  theme_classic() %+replace%
    
    theme(
      panel.grid.major = element_blank(),
      panel.grid.minor = element_blank(),
      plot.margin = margin(2, 0, 2, 0), 
      
      text = element_text(size = baseFontSize), 
      line = element_line(linewidth = baseLineWidth), 

      # axis.line = element_line(color = "black", linewidth = baseLineWidth),
      # axis.ticks = element_line(color = "black", linewidth = baseLineWidth),
      axis.ticks.length = unit(baseLineWidth * 2, "mm"),
      
      
      axis.title = element_text(
        family = font,
        face = "bold",
        size = baseFontSize
      ),
      
      axis.text = element_text(
        family = font,
        face = "bold",
        size = baseFontSize * 0.8
      ),
      
      legend.title = element_text(
        family = font,
        face = "bold",
        size = baseFontSize
      ),
      
      legend.text = element_text(
        family = font,
        face = "bold",
        size = baseFontSize * 0.8
      ),
      
      strip.placement = "outside", 
      strip.background = element_blank(),
      strip.text = element_text(
        family = font,
        face = "bold",
        size = baseFontSize
      )
    )
}

cropBlot <- function(target, imgPath, x, y, width, height, ...) {
  library(magick)
  
  format <- "tif"
  
  img <- image_read(imgPath)
  imgInfo <- image_info(img)
  imgWidth <- imgInfo$width
  imgHeight <- imgInfo$height
  
  cropWidth <- imgWidth * width
  cropHeight <- imgHeight * height
  
  xOff <- x * imgWidth
  yOff <- y * imgHeight
  
  imgCropped <-
    image_crop(img, glue("{cropWidth}x{cropHeight}+{xOff}+{yOff}>"))
  
  # ggpattern calls gridpattern:::img_read. The function requires image to have 4 channels. 
  # When magick::image::write is called to write PNG, optimization collapses RGB to grayscale as the blot has only grayscale information. 
  # This behavior doesn't seem to be overridden in R. 
  
  imgCropped <- image_convert(imgCropped, format = format, type = "truecolor", colorspace = "sRGB")
  
  imgSavePath <-
    gsub(paste0(".", tools::file_ext(imgPath)), paste0("_", target), imgPath)
  
  image_write(imgCropped, paste0(imgSavePath, ".", format), format = format)
  return(paste0(imgSavePath, ".", format))
}

pltSpacer <- plot_spacer() + theme(plot.margin = margin(0, 0, 0, 0))

# stdError <- function(x) sd(x)/sqrt(length(x))

getStatAnnotTbl <- function(dfData, dfStat){
  Ypad <-  (fontSize/ggplot2::.pt+2) * max(dfData$Value) * 0.025

  dfStat <- dfStat %>%
    arrange(Group1, Group2) %>%
    mutate(
      Ypad = Ypad, 
      Ymin1 = map_dbl(Group1, function(x) {
        dfData %>% filter(Group == x) %>% pull(Value) %>% max()
        }), 
      Ymin2 = map_dbl(Group2, function(x) {
        dfData %>% filter(Group == x) %>% pull(Value) %>% max()
        }),
      Ymax = map2_dbl(Group1, Group2, function(x, y){
        dfData %>% filter(Group >= x & Group <= y) %>% pull(Value) %>% max()
        })
      ) %>%
    rowwise() %>%
    mutate(
      Ymin1 = Ymin1 + Ypad / 2, 
      Ymin2 = Ymin2 + Ypad / 2, 
      X = sum(which(levels(dfData$Group) %in% c(Group1, Group2)))/2
    )

  if (nrow(dfStat) > 1) {
    for (i in 2:nrow(dfStat)){
      for (j in 1:(i-1)){
        if (dfStat$Ymax[i] <= dfStat$Ymax[j] + Ypad){
          if ((dfStat$Group2[j] > dfStat$Group1[i] | dfStat$Group2[j] > dfStat$Group1[i])) {
            dfStat[i, "Ymax"] <- dfStat$Ymax[i-1] + Ypad
          }
        }
      }
    }    
  }
  
  dfStat <- dfStat %>%
    mutate(
      YmaxAdj = Ymax + Ypad,
      XAdj = X
    )
  
  for (i in 1:nrow(dfStat)){
      dfStat[i, "XAdj"] <- dfStat$XAdj[i]
    if (floor(dfStat$XAdj[i]) == dfStat$XAdj[i]) {
      if (levels(dfData$Group)[as.integer(dfStat$XAdj[i])] %in% c(dfStat$Group1, dfStat$Group2)){
        dfStat[i, "XAdj"] <-  dfStat$XAdj[i]-1/length(levels(dfData$Group))
      }
    }
  }
  
  return(dfStat)
}
```

# **Panel A: Representative blots**

Letter paper size: 8.5 in * 11 in
Plos One figure size: width 2.63 in - 7.5 in; single column figure width <= 5.2 in; height <= 8.75
Text within figures: 8-12 pt. 

## Representative blot

```{r fig.height=1.6, fig.width=3.75}
blnForget <- memoise::forget(gridpattern:::img_read_memoised)

row_margin <- 0.15

dfBlot <- data.frame(
  target = c("CYB5R4", "GFP", "aTubulin")
) %>%
  mutate(
    target = factor(target, levels = target), 
    imgPath = c(
      glue("{root_dir}/20230223_HAEC_pCIGX-R4_MRT67307_Withdrawal/20230223_CYB5R4_GFP.tif"), 
      glue("{root_dir}/20230223_HAEC_pCIGX-R4_MRT67307_Withdrawal/20230223_CYB5R4_GFP.tif"), 
      glue("{root_dir}/20230223_HAEC_pCIGX-R4_MRT67307_Withdrawal/20230223_aTub.tif")),
    x = c(0.07, 0.07, 0.06), 
    y = c(0.36, 0.65, 0.78), 
    width = c(0.84, 0.84, 0.85), 
    height = c(0.15, 0.15, 0.15), 
    lane = 12, 
    col_width = height / min(height) - row_margin
  )
for (idx in 1:nrow(dfBlot)){
  if (idx == 1) {
    dfBlot[idx, "col_x"] <- 1
  } else {
    dfBlot[idx, "col_x"] <- dfBlot[idx-1, "col_x"] +sum(dfBlot[(idx-1):idx, "col_width"]) / 2 + row_margin
  }
}

vtSample <- c(1:12)

imgCropped <- pmap_chr(dfBlot, cropBlot)
dfBlot$cropped <- imgCropped
names(imgCropped) <- dfBlot$target

pltBlot <- dfBlot %>%
  ggplot(aes(x = col_x, y = lane, width = col_width)) + 
  geom_col_pattern(
    aes(pattern_filename = target), 
    pattern = "image",
    pattern_type = "squish",
    color = "black",
    linewidth = lineWidth, 
    pattern_scale = 1
  ) +
  scale_pattern_filename_manual(values = imgCropped) +
  labs(x = NULL, y = NULL) +
  scale_y_continuous(position = "left", limits = c(0, length(vtSample)), breaks = c(1:length(vtSample) - 0.5), labels = vtSample, expand = c(0, 0)) +
  coord_flip(clip = "off") +
  scale_x_reverse(limits = rev(c(dfBlot[1, "col_x"] - dfBlot[1, "col_width"]/2, dfBlot[nrow(dfBlot), "col_x"] + dfBlot[nrow(dfBlot), "col_width"]/2)), breaks = dfBlot$col_x, labels = dfBlot$target) +
  theme_yuan_wb(baseFontSize = fontSize) +
  theme(
    plot.margin = margin(0, 0, 0, 0), 
    axis.text.x = element_blank()
  )

pltMw <- data.frame(col_x = dfBlot$col_x,
                    kDa = c(55, 27, 51)) %>%
  ggplot(aes(x = 0, y = col_x, label = kDa)) +
  geom_text(size = ggplot2::.pt) +
  labs(x = "kDa", y = NULL) +
  scale_y_reverse(
    limits = rev(c(dfBlot[1, "col_x"] - dfBlot[1, "col_width"] / 2, dfBlot[nrow(dfBlot), "col_x"] + dfBlot[nrow(dfBlot), "col_width"] / 2)),
    breaks = dfBlot$col_x) +
  scale_x_discrete(position = "top") +
  coord_cartesian(clip = "off") +
  theme_yuan_wb(baseFontSize = fontSize) +
  theme(axis.text.x = element_blank(),
        axis.text.y = element_blank())

pltTbl <- data.frame(
  sample = vtSample, 
  "pCIGX-CYB5R4 (ug)" = rep(c(0, 0.2, 0.4) %>% as.character(), each = 4), 
  "MRT67307 (5uM, hrs)" = rep(c("0", "0-4", "0-24", "0-48"), times = 3), 
  check.names = FALSE) %>%
  mutate(sample = factor(vtSample, levels = vtSample)) %>%
  pivot_longer(cols = names(.)[2:ncol(.)], names_to = "treatment") %>%
  ggplot(aes(x = sample, y = treatment, label = value)) +
  geom_text(angle = 45, size = ggplot2::.pt) +
  labs(y = NULL, x = NULL) +
  theme_yuan_wb(baseFontSize = fontSize) +
  theme(
    axis.text.x = element_blank(),
    plot.margin = margin(0, 0, 0, 0)
    # panel.border = element_rect(fill = NA, color = "black")
  )

pltBlotRm <- (pltBlot + pltMw + plot_layout(widths = c(9, 0.5))) / (pltTbl + pltSpacer + plot_layout(widths = c(9, 0.5))) + plot_layout(heights = c(1, 0.6))
pltBlotRm <- pltSpacer - pltBlotRm + plot_layout(widths = c(0, 1))

show(pltBlotRm)
```

## Panel B: Quantification

```{r, fig.height=3, fig.width=3.75}
file.list <- list.files(root_dir, pattern = "\\.xlsx$", full.names = TRUE, recursive = TRUE)
file.list <- file.list[grepl("Withdrawal", file.list, perl = TRUE)]
file.list <- file.list[grepl("HAEC", file.list)]

dfData <- map_dfr(file.list, read.xlsx) %>%
  # filter(Transfection.Hour == 4) %>%
  arrange(Date) %>%
  mutate(
    Target = fct_inorder(Target), 
    Inhibitor.Name = fct_inorder(Inhibitor.Name), 
    Inhibitor.Duration.Hour = as.character(Inhibitor.Duration.Hour), 
    Inhibitor.Duration.Hour = fct_inorder(Inhibitor.Duration.Hour), 
    Group = ordered(Inhibitor.Duration.Hour)
    ) %>%
  arrange(Date, Target, Lane) %>%
  group_by(Date) %>%
  mutate(
    Signal.Norm = Signal / Signal[Target == "a-Tubulin"]
  ) %>%
  group_by(Date, Target) %>%
  mutate(
    Value = Signal.Norm / Signal.Norm[Lane == 5]
  )

dfStat <- dfData %>%
  filter(Target != "a-Tubulin") %>%
  group_by(Plasmid.uM, Target) %>%
  nest() %>%
  mutate(
    model = map(data, function(x) aov(Value ~ Group, data = x)),
    Anova.pvalue = map_dbl(model, function(x) summary(x)[[1]]$`Pr(>F)`[1])
    # model = map(data, function(x) lmer(Value ~ Group + (1|Date), data = x)),
    # Anova.pvalue = map_dbl(model, function(x) anova(x)$`Pr(>F)`[1])
  ) %>%
  filter(Anova.pvalue < 0.05) %>%
  mutate(
    post.hoc = map2(data, model, function(x, y){
      emm <- emmeans(y, ~ Group)
      dfPostHoc <- contrast(emm, "pairwise", adjust = "tukey") %>%
        as.data.frame() %>%
        rename(c("Contrast" = "contrast")) %>%
        # The groups need to be in the levels of dfData$Group.
        # Group1 and Group2 are two factors sharing the same order as dfData$Group. 
        mutate(
          Contrast = as.character(Contrast) %>%
            str_replace_all(c("^\\(" = "", "\\)$" = "", "\\) - \\(" = "SPLIT", " - \\(" = "SPLIT", "\\) - " = "SPLIT", " - " = "SPLIT")), 
          Group1 = map_vec(Contrast, function(x) {
            str_split_1(x, "SPLIT") %>% 
              ordered(levels = levels(dfData$Group)) %>%
              min()
            }),
          Group2 = map_vec(Contrast, function(x) {
            vt <- str_split_1(x, "SPLIT") %>% 
              ordered(levels = levels(dfData$Group)) %>%
              max()
            }),
          Contrast = str_replace_all(Contrast, c("SPLIT" = " vs "))
          ) %>%
        # Post-hoc table should be cleaned up before coordinates are calculated. 
        filter(p.value < 0.05)

      if (nrow(dfPostHoc) == 0) return()

      getStatAnnotTbl(x, dfPostHoc)
    })
  ) %>%
  unnest(cols = c("post.hoc")) %>%
  ungroup()

vtLabs <- paste("Plasmid", c(0.2, 0.4), "ug")
names(vtLabs) <- c("0.2", "0.4")

pltBarAdd <- dfData %>%
  filter(Target != "a-Tubulin", Plasmid.uM > 0) %>%
  ggplot(aes(x = Group, y = Value)) +
  stat_summary(aes(fill = Group), geom = "col", fun.data = "mean_se", color = "black", linewidth = lineWidth) +
  stat_summary(geom = "errorbar", fun.data = "mean_se", width = 0.5, linewidth = lineWidth) +
  scale_fill_brewer(palette = "Set3") +
  geom_point(size = 1, show.legend = FALSE) +
  facet_wrap(~ Plasmid.uM + Target, scale = "free", strip.position = "left", labeller = labeller(Plasmid.uM = vtLabs)) +
  labs(y = NULL, x = NULL, fill = "Hour:") +
  coord_cartesian(clip = "off") +
  scale_y_continuous(expand = expansion(mult = c(0, 0.1))) +
  guides(fill = guide_legend(nrow = 1)) +
  theme_yuan() +
  theme(
    axis.text.x = element_blank(), 
    axis.ticks.x = element_blank(), 
    legend.position = "bottom",
    # legend.title = element_blank(), 
    legend.key.size = unit(3, "mm")
  )

if (nrow(dfStat) > 0) {
  pltBarAdd <- pltBarAdd  +
    geom_segment(data = dfStat, aes(x = Group1, y = YmaxAdj, xend = Group2, yend = YmaxAdj), linewidth = lineWidth) +
    geom_segment(data = dfStat, aes(x = Group1, y = Ymin1, xend = Group1, yend = YmaxAdj), linewidth = lineWidth) +
    geom_segment(data = dfStat, aes(x = Group2, y = Ymin2, xend = Group2, yend = YmaxAdj), linewidth = lineWidth) +
    geom_text(data = dfStat, aes(x = XAdj, y = YmaxAdj + Ypad * 0.1, label = ifelse(p.value < 0.05, "*", "")), size = fontSize/ggplot2::.pt+2)
  }

pltBarRm <- pltSpacer+ pltBarAdd + plot_layout(widths = c(0, 1))

pltBarRm
```

# Figure 3 Assembly

```{r fig.height=4.6, fig.width=3.75}
((pltBlotRm & theme(plot.tag.position = c(0.01, 0.9))) - (pltBarRm & theme(plot.tag.position = c(0, 1)))) +
  plot_layout(heights = c(1.8, 3)) +
  plot_annotation(tag_levels = list(c("A", "", "",
                                 "B"))) &
  theme(
    plot.background = element_blank(), 
    plot.tag = element_text(face = "bold")
    )

ggsave("Figure_3_v1.1.pdf", width = 3.75, height = 4.6, dpi = 600)
```

