---
title: "Plasmid OE with STING Inhibition"
subtitle: "Figure 4: MRT67307 effects on transfection are reversible"
author: "Shuai Yuan"
date: '`r format(Sys.Date(), "%Y-%m-%d")`'
output: 
  html_document:
    toc: true
    toc_float: true
    toc_depth: 5
    number_sections: true
---

```{r setup, echo = FALSE}
options(
  htmltools.dir.version = FALSE, 
  knitr.duplicate.label = "allow", 
  ggpattern_res = 1200
  )
knitr::opts_chunk$set(
  dpi = 300, 
  out.width = "100%",
  cache = FALSE,
  echo = FALSE,
  message = FALSE, 
  warning = FALSE,
  hiline = TRUE
  )

root_dir <- "../Data/WB"
```

```{r pkgs}
library(lmerTest)
library(emmeans)

library(openxlsx)
library(tidyverse)
library(magrittr)
library(extrafont)
library(glue)
library(ggpattern)
library(ggupset)
library(patchwork)
# library(ggtext)

# Define ggplot theme

fontSize <- 10
lineWidth <- 0.4 # also used in setting geom with linewidth. 

theme_yuan_wb <- function(baseFontSize = fontSize, baseLineWidth = lineWidth) {
  font <- "serif"
  
  theme_classic() %+replace%
    
    theme(
      panel.grid = element_blank(),
      panel.border = element_blank(),
      plot.background = element_blank(), 
      plot.margin = margin(0, 0, 0, 0), 
      
      axis.line = element_blank(),
      axis.ticks = element_blank(),

      text = element_text(size = baseFontSize), 
      line = element_line(linewidth = baseLineWidth), 
      
      axis.text.x = element_text(angle = 45, hjust = 0),
      legend.position = 'none',
      # aspect.ratio = 0.25,
      
      title = element_text(
        family = font,
        face = "bold",
        size = baseFontSize
      ),
      
      axis.title = element_text(
        family = font,
        face = "bold",
        size = baseFontSize
      ),
      
      axis.text = element_text(
        family = font,
        face = "bold",
        size = baseFontSize * 0.8
      ),
      
      legend.title = element_text(
        family = font,
        face = "bold",
        size = baseFontSize
      ),
      
      legend.text = element_text(
        family = font,
        face = "bold",
        size = baseFontSize * 0.8
      ),
      
      strip.background = element_blank(),
      strip.placement = "outside", 
      strip.text = element_text(
        family = font,
        face = "bold",
        size = baseFontSize
      )
    )
}

theme_yuan <- function(baseFontSize = fontSize, baseLineWidth = lineWidth) {
  font <- "sans"
  
  theme_classic() %+replace%
    
    theme(
      panel.grid.major = element_blank(),
      panel.grid.minor = element_blank(),
      plot.margin = margin(2, 0, 2, 0), 
      
      text = element_text(size = baseFontSize), 
      line = element_line(linewidth = baseLineWidth), 

      # axis.line = element_line(color = "black", linewidth = baseLineWidth),
      # axis.ticks = element_line(color = "black", linewidth = baseLineWidth),
      axis.ticks.length = unit(baseLineWidth * 2, "mm"),
      
      
      axis.title = element_text(
        family = font,
        face = "bold",
        size = baseFontSize
      ),
      
      axis.text = element_text(
        family = font,
        face = "bold",
        size = baseFontSize * 0.8
      ),
      
      legend.title = element_text(
        family = font,
        face = "bold",
        size = baseFontSize
      ),
      
      legend.text = element_text(
        family = font,
        face = "bold",
        size = baseFontSize * 0.8
      ),
      
      strip.placement = "outside", 
      strip.background = element_blank(),
      strip.text = element_text(
        family = font,
        face = "bold",
        size = baseFontSize
      )
    )
}

cropBlot <- function(target, imgPath, x, y, width, height, ...) {
  library(magick)
  
  format <- "tif"
  
  img <- image_read(imgPath)
  imgInfo <- image_info(img)
  imgWidth <- imgInfo$width
  imgHeight <- imgInfo$height
  
  cropWidth <- imgWidth * width
  cropHeight <- imgHeight * height
  
  xOff <- x * imgWidth
  yOff <- y * imgHeight
  
  imgCropped <-
    image_crop(img, glue("{cropWidth}x{cropHeight}+{xOff}+{yOff}>"))
  
  # ggpattern calls gridpattern:::img_read. The function requires image to have 4 channels. 
  # When magick::image::write is called to write PNG, optimization collapses RGB to grayscale as the blot has only grayscale information. 
  # This behavior doesn't seem to be overridden in R. 
  
  imgCropped <- image_convert(imgCropped, format = format, type = "truecolor", colorspace = "sRGB")
  
  imgSavePath <-
    gsub(paste0(".", tools::file_ext(imgPath)), paste0("_", target), imgPath)
  
  image_write(imgCropped, paste0(imgSavePath, ".", format), format = format)
  return(paste0(imgSavePath, ".", format))
}

pltSpacer <- plot_spacer() + theme(plot.margin = margin(0, 0, 0, 0))

# stdError <- function(x) sd(x)/sqrt(length(x))

getStatAnnotTbl <- function(dfData, dfStat){
  Ypad <-  (fontSize/ggplot2::.pt+2) * max(dfData$Value) * 0.025

  dfStat <- dfStat %>%
    arrange(Group1, Group2) %>%
    mutate(
      Ypad = Ypad, 
      Ymin1 = map_dbl(Group1, function(x) {
        dfData %>% filter(Group == x) %>% pull(Value) %>% max()
        }), 
      Ymin2 = map_dbl(Group2, function(x) {
        dfData %>% filter(Group == x) %>% pull(Value) %>% max()
        }),
      Ymax = map2_dbl(Group1, Group2, function(x, y){
        dfData %>% filter(Group >= x & Group <= y) %>% pull(Value) %>% max()
        })
      ) %>%
    rowwise() %>%
    mutate(
      Ymin1 = Ymin1 + Ypad / 2, 
      Ymin2 = Ymin2 + Ypad / 2, 
      X = sum(which(levels(dfData$Group) %in% c(Group1, Group2)))/2
    )

  if (nrow(dfStat) > 1) {
    for (i in 2:nrow(dfStat)){
      for (j in 1:(i-1)){
        if (dfStat$Ymax[i] <= dfStat$Ymax[j] + Ypad){
          if ((dfStat$Group2[j] > dfStat$Group1[i] | dfStat$Group2[j] > dfStat$Group1[i])) {
            dfStat[i, "Ymax"] <- dfStat$Ymax[i-1] + Ypad
          }
        }
      }
    }    
  }
  
  dfStat <- dfStat %>%
    mutate(
      YmaxAdj = Ymax + Ypad,
      XAdj = X
    )
  
  for (i in 1:nrow(dfStat)){
      dfStat[i, "XAdj"] <- dfStat$XAdj[i]
    if (floor(dfStat$XAdj[i]) == dfStat$XAdj[i]) {
      if (levels(dfData$Group)[as.integer(dfStat$XAdj[i])] %in% c(dfStat$Group1, dfStat$Group2)){
        dfStat[i, "XAdj"] <-  dfStat$XAdj[i]-1/length(levels(dfData$Group))
      }
    }
  }
  
  return(dfStat)
}
```

# **Panel A: Representative blots**

Letter paper size: 8.5 in * 11 in
Plos One figure size: width 2.63 in - 7.5 in; single column figure width <= 5.2 in; height <= 8.75
Text within figures: 8-12 pt. 

## Representative blot

```{r fig.height=1.3, fig.width=2.8}
blnForget <- memoise::forget(gridpattern:::img_read_memoised)

row_margin <- 0.15

dfBlot <- data.frame(
  target = c("eNOS pS1177", "eNOS", "GFP", "aTubulin")
) %>%
  mutate(
    target = factor(target, levels = target), 
    imgPath = c(
      glue("{root_dir}/20230630_HAEC_eNOS.OE.WT.S1177A_VEGF_20ng.ml/20230630_eNOS.pS1177.tif"), 
      glue("{root_dir}/20230630_HAEC_eNOS.OE.WT.S1177A_VEGF_20ng.ml/20230630_eNOS.tif"), 
      glue("{root_dir}/20230630_HAEC_eNOS.OE.WT.S1177A_VEGF_20ng.ml/20230630_GFP.tif"), 
      glue("{root_dir}/20230630_HAEC_eNOS.OE.WT.S1177A_VEGF_20ng.ml/20230630_aTub.tif")),
    x = c(0.15, 0.15, 0.12, 0.14), 
    y = c(0.05, 0.05, 0.65, 0.4), 
    width = c(0.83, 0.83, 0.83, 0.83), 
    height = c(0.1, 0.1, 0.1, 0.1), 
    lane = 6, 
    col_width = height / min(height) - row_margin
  )

for (idx in 1:nrow(dfBlot)){
  if (idx == 1) {
    dfBlot[idx, "col_x"] <- 1
  } else {
    dfBlot[idx, "col_x"] <- dfBlot[idx-1, "col_x"] +sum(dfBlot[(idx-1):idx, "col_width"]) / 2 + row_margin
  }
}

vtSample <- c(1:6)

imgCropped <- pmap_chr(dfBlot, cropBlot)
dfBlot$cropped <- imgCropped
names(imgCropped) <- dfBlot$target

pltBlot <- dfBlot %>%
  ggplot(aes(x = col_x, y = lane, width = col_width)) + 
  geom_col_pattern(
    aes(pattern_filename = target), 
    pattern = "image",
    pattern_type = "squish",
    color = "black",
    linewidth = lineWidth, 
    pattern_scale = 1
  ) +
  scale_pattern_filename_manual(values = imgCropped) +
  labs(x = NULL, y = NULL) +
  scale_y_continuous(position = "left", limits = c(0, length(vtSample)), breaks = c(1:length(vtSample) - 0.5), labels = vtSample, expand = c(0, 0)) +
  coord_flip(clip = "off") +
  scale_x_reverse(limits = rev(c(dfBlot[1, "col_x"] - dfBlot[1, "col_width"]/2, dfBlot[nrow(dfBlot), "col_x"] + dfBlot[nrow(dfBlot), "col_width"]/2)), breaks = dfBlot$col_x, labels = dfBlot$target) +
  theme_yuan_wb(baseFontSize = fontSize) +
  theme(
    axis.text.x = element_blank()
  )

pltBlot

pltMw <- data.frame(col_x = dfBlot$col_x,
                    kDa = c(133, 133, 27, 51)) %>%
  ggplot(aes(x = 0, y = col_x, label = kDa)) +
  geom_text(size = ggplot2::.pt) +
  labs(x = "kDa", y = NULL) +
  scale_y_reverse(
    limits = rev(c(dfBlot[1, "col_x"] - dfBlot[1, "col_width"] / 2, dfBlot[nrow(dfBlot), "col_x"] + dfBlot[nrow(dfBlot), "col_width"] / 2)),
    breaks = dfBlot$col_x) +
  scale_x_discrete(position = "top") +
  coord_cartesian(clip = "off") +
  theme_yuan_wb(baseFontSize = fontSize) +
  theme(axis.text.x = element_blank(),
        axis.text.y = element_blank())

pltBlotNos <- (pltBlot + pltMw + plot_layout(widths = c(9, 0.5)))

show(pltBlotNos)
```

## Panel A: Quantification

```{r, fig.height=3.2, fig.width=2.8}
file.list <- list.files(root_dir, pattern = "\\.xlsx$", full.names = TRUE, recursive = TRUE)
file.list <- file.list[grepl("eNOS", file.list)]

dfData <- map_dfr(file.list, read.xlsx) %>%
  filter(Rep == 1) %>%
  arrange(Date) %>%
  rename(Minute = "VEGF.20ng/ml.(minutes)") %>%
  mutate(
    Target = fct_inorder(Target), 
    Plasmid = fct_inorder(Plasmid), 
    Group = paste(Plasmid, Minute), 
    Group = fct_inorder(Group) %>% ordered()
    ) %>%
  arrange(Date, Rep, Minute, Plasmid, Target, Lane) %>%
  group_by(Date, Rep) %>%
  mutate(
    Signal.Norm = Signal / Signal[Target == "a-Tubulin"]
  ) %>%
  group_by(Date, Rep, Target) %>%
  mutate(
    Value = Signal.Norm / Signal.Norm[Plasmid == "pCIGX-MCS" & Minute == 0]
  )

dfStat <- dfData %>%
  filter(Target != "a-Tubulin") %>%
  group_by(Rep, Target) %>%
  nest() %>%
  mutate(
    # model = map(data, function(x) aov(Value ~ Group, data = x)),
    # Anova.pvalue = map_dbl(model, function(x) summary(x)[[1]]$`Pr(>F)`[1])
    model = map(data, function(x) lmer(Value ~ Group + (1|Date), data = x)),
    Anova.pvalue = map_dbl(model, function(x) anova(x)$`Pr(>F)`[1])
  ) %>%
  filter(Anova.pvalue < 0.05) %>%
  mutate(
    post.hoc = map2(data, model, function(x, y){
      emm <- emmeans(y, ~ Group)
      dfPostHoc <- contrast(emm, "pairwise", adjust = "tukey") %>%
        as.data.frame() %>%
        rename(c("Contrast" = "contrast")) %>%
        # The groups need to be in the levels of dfData$Group.
        # Group1 and Group2 are two factors sharing the same order as dfData$Group. 
        mutate(
          Contrast = as.character(Contrast) %>%
            str_replace_all(c("^\\(" = "", "\\)$" = "", "\\) - \\(" = "SPLIT", " - \\(" = "SPLIT", "\\) - " = "SPLIT", " - " = "SPLIT")), 
          Group1 = map_vec(Contrast, function(x) {
            str_split_1(x, "SPLIT") %>% 
              ordered(levels = levels(dfData$Group)) %>%
              min()
            }),
          Group2 = map_vec(Contrast, function(x) {
            vt <- str_split_1(x, "SPLIT") %>% 
              ordered(levels = levels(dfData$Group)) %>%
              max()
            }),
          Contrast = str_replace_all(Contrast, c("SPLIT" = " vs "))
          ) %>%
        # Post-hoc table should be cleaned up before coordinates are calculated. 
        filter(p.value < 0.05) %>% 
        mutate(
          Group1.Plasmid = map_chr(Group1, function(x) strsplit(as.character(x), " ") %>% unlist() %>% first()), 
          Group1.Minute = map_chr(Group1, function(x) strsplit(as.character(x), " ") %>% unlist() %>% last()), 
          Group2.Plasmid = map_chr(Group2, function(x) strsplit(as.character(x), " ") %>% unlist() %>% first()), 
          Group2.Minute = map_chr(Group2, function(x) strsplit(as.character(x), " ") %>% unlist() %>% last())
          ) %>%
      filter(
        Group1.Minute == Group2.Minute |
          Group1.Plasmid == Group2.Plasmid
      )

      if (nrow(dfPostHoc) == 0) return()

      getStatAnnotTbl(x, dfPostHoc)
    })
  ) %>%
  unnest(cols = c("post.hoc")) %>%
  ungroup()

lstPltBar <- dfData %>%
  filter(!Target %in% c("a-Tubulin", "Akt pS473")) %>%
  group_by(Target) %>%
  nest() %>%
  mutate(
    plt = map(data, function(df){
      p <- ggplot(df, aes(x = Group, y = Value)) +
        stat_summary(aes(fill = Group), geom = "col", fun.data = "mean_se", color = "black", linewidth = lineWidth) +
        stat_summary(geom = "errorbar", fun.data = "mean_se", width = 0.5, linewidth = lineWidth) +
        scale_fill_brewer(palette = "Set3") +
        annotation_custom(grob = grid::textGrob(label = glue("{unique(Target)}\n(Fold Change)"), rot = 90,  gp = grid::gpar(fontsize = 8, fontface = "bold"), x = -30, default.units = "pt")) + 
        geom_point(size = 1) +
        guides(fill = FALSE) +
        coord_cartesian(clip = "off") +
        scale_y_continuous(expand = expansion(mult = c(0, 0.1))) +
        theme_yuan(baseFontSize = 10) +
        theme(
          axis.text.x = element_blank(),
          axis.ticks.x = element_blank(), 
          axis.title = element_blank()
        )
      
      if (nrow(dfStat) > 0) {
        p <- p  +
          geom_segment(data = dfStat[dfStat$Target == unique(Target), ], aes(x = Group1, y = YmaxAdj, xend = Group2, yend = YmaxAdj), linewidth = lineWidth) +
          geom_segment(data = dfStat[dfStat$Target == unique(Target), ], aes(x = Group1, y = Ymin1, xend = Group1, yend = YmaxAdj), linewidth = lineWidth) +
          geom_segment(data = dfStat[dfStat$Target == unique(Target), ], aes(x = Group2, y = Ymin2, xend = Group2, yend = YmaxAdj), linewidth = lineWidth) +
          geom_text(data = dfStat[dfStat$Target == unique(Target), ], aes(x = XAdj, y = YmaxAdj + Ypad * 0.1, label = ifelse(p.value < 0.05, "*", "")), size = fontSize/ggplot2::.pt+2)
      }
      
      p <- p + pltSpacer + plot_layout(widths = c(9, 0.5))
    })
  ) %>%
  ungroup %>%
  select(plt) %>%
  unlist(recursive = FALSE, use.names = TRUE)

pltBarNos <- wrap_plots(lstPltBar, ncol = 1)

pltBarNos
```

## Legend

```{r fig.height=0.8, fig.width=2.8}
pltTbl <- data.frame(
  sample = vtSample, 
  Plasmid = rep(c("EV", "WT", "S1177A") %>% as.character(), times = 2), 
  VEGF = rep(c("-", "+"), each = 3), 
  check.names = FALSE) %>%
  mutate(sample = factor(vtSample, levels = vtSample)) %>%
  pivot_longer(cols = names(.)[2:ncol(.)], names_to = "treatment") %>%
  mutate(ang = rep(c(45, 0), times = 6)) %>%
  ggplot(aes(x = sample, y = treatment, label = value)) +
  geom_text(aes(angle = ang), size = ggplot2::.pt) +
  labs(y = NULL, x = NULL) +
  coord_cartesian(clip = "off") +
  theme_yuan_wb(baseFontSize = fontSize) +
  theme(
    axis.text.x = element_blank(),
    plot.margin = margin(0, 0, 0, 0)
    # panel.border = element_rect(fill = NA, color = "black")
  )

pltTblNos <- (pltTbl + pltSpacer) + plot_layout(widths = c(9, 0.5))

show(pltTblNos)
```

# Panel A Assembly

```{r fig.height=4.6, fig.width=2.8}
# pltA <- (pltBlotNos/ pltBarNos / pltTblNos +
#           plot_layout(heights = c(1.3, 3.2, 0.8)) +
#           plot_annotation(tag_levels = list(c("A", "", "", "", "", "")))) &
#           theme(
#             plot.background = element_blank(), 
#             plot.tag = element_text(face = "bold")
#             )

pltA <- (pltBlotNos/ pltBarNos / pltTblNos +
          plot_layout(heights = c(1.3, 3.2, 0.8)))

pltA
# ggsave("Figure_4.pdf", width = 3.75, height = 4.6, dpi = 600)
```

```{r}
library(magick)
library(tidyverse)
library(ggtext)

dfImg <- data.frame(
  title = c("EV", "WT", "S1177A"), 
  path = c("../Data/ICC/MAX_20230705_EV.OE.VEGF_DAPI_488-GFP_594-eNOS.pS1177_647-eNOS_40X_1.tif_Montage.tif", 
           "../Data/ICC/MAX_20230705_eNOS.WT.OE.VEGF_DAPI_488-GFP_594-eNOS.pS1177_647-eNOS_40X_2.tif_Montage.tif", 
           "../Data/ICC/MAX_20230705_eNOS.S1177A.OE.VEGF_DAPI_488-GFP_594-eNOS.pS1177_647-eNOS_40X_1.tif_Montage.tif")
)

dfLabs <- data.frame(x = c(10, 1040, 2080), y = rep(1020, 3), text = c("<span style='color:blue'>**DAPI**</span><br><span style='color:green'>**GFP**</span>", "<span style='color:blue'>**DAPI**</span><br><span style='color:red'>**eNOS pS1177**</span>", "<span style='color:blue'>**DAPI**</span><br><span style='color:white'>**eNOS**</span>"))

lstPltIcc <- dfImg %>%
  group_by(title) %>%
  nest() %>%
  mutate(
    plt = map(data, function(df){
      p <- image_ggplot(image_read(df$path)) +
        labs(y = title) +
        theme_yuan(baseFontSize = 10) +
        theme(
          axis.text.x = element_blank(),
          axis.ticks.x = element_blank(), 
          axis.text.y = element_blank(),
          axis.ticks.y = element_blank(), 
          axis.title.x = element_blank()
        )
      if (title == "EV") p <- p + geom_richtext(data = dfLabs, aes(x = x, y = y, label = text), fill = "black", vjust = 1, hjust = 0, alpha = 0.5, size = ggplot2::.pt)
      return (p)
    })
  ) %>%
  ungroup %>%
  select(plt) %>%
  unlist(recursive = FALSE, use.names = TRUE)

pltB <- wrap_plots(lstPltIcc, ncol = 1)

pltB
```

# Figure 5 Assembly

```{r fig.height=4.6, fig.width=7.4}
(((pltA & theme(plot.tag.position = c(0, 0.94))) | pltB & theme(plot.tag.position = c(0.02, 1.08), plot.margin = margin(0, 0, 0, 10))) + plot_layout(widths = c(2.8, 4.6)) +
  plot_annotation(tag_levels = list(c("A", "", "", "", "", "", "B", "", "")))) &
  theme(
    plot.background = element_blank(), 
    plot.tag = element_text(face = "bold")
    )


ggsave("Figure_5_v1.1.pdf", width = 7.4, height = 4.6, dpi = 600)
```
